---
title: "Saptari_outline"
output: pdf_document
---

```{r setup, include=FALSE}
library(dplyr)
library(kableExtra)
library(formattable)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

land_17_18_19 <- read.csv("~/R/Saptari/data/land_17_18_19.csv")
Agriculture_17_18_19 <- read.csv("~/R/Saptari/data/Agriculture_17_18_19.csv")

```

4. LAND

5. AGRICULTURE 

6.2 WEM

7. PROCUREMENT




total_ownland_cultivated
```{r total_ownland_cultivated, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

lso <- land_17_18_19%>% 
  filter(total_land_cultivated_year>0) %>%
  group_by(year,TreatmentControl, household_questionnaire_id) %>%
  summarise(own=sum(total_ownland_cultivated)*0.0338) %>% 
  group_by(TreatmentControl,year) %>%
  summarise(N=n(), Mean=mean(own)) %>% 
  mutate(across(is.numeric, round, 2))

lsoC <- lso[1:3,-1]
lsoT <- lso[4:6,3:4]
lsoC_lsoT <- cbind(lsoC,lsoT)


kable(lsoC_lsoT, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
column_spec(1, bold = T) %>%
kable_styling(latex_options = "striped", position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>%column_spec(3,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
&nbsp;

&nbsp;

total_land_cultivated
```{r total_land_cultivated,echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE }

lsc <- land_17_18_19%>% 
  filter(total_land_cultivated_year>0) %>%
  group_by(year,TreatmentControl, household_questionnaire_id) %>%
  summarise(cult=sum(total_land_cultivated)*0.0338) %>% 
  group_by(TreatmentControl,year) %>%
  summarise(N=n(), Mean=mean(cult)) %>% 
  mutate(across(is.numeric, round, 2))


lscC <- lsc[1:3,-1]
lscT <- lsc[4:6,3:4]
lscC_lscT <- cbind(lscC,lscT)

kable(lscC_lscT, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
column_spec(1, bold = T) %>%
kable_styling(latex_options = "striped", position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>%column_spec(3,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")
```
&nbsp;

&nbsp;

Crop Intensity
```{r  Cropping Intensity, echo=FALSE}

crop_intensity <- tribble(~" ",~N ,~mean,~N,~mean, 2017,91,"229%",22,"196%",2018,91,"215%",22,"188%",2019,84,"193%",23,"152%")

kable(crop_intensity, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
2017,91,"229%",22,"196%",2018,91,"215%",22,"188%",2019,84,"193%",23,"152%"


## Irrigation

irrigated_out_of_tot_land_cult [4.9]
```{r irrigated_out_of_tot_land_cult [4.9], echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE }
lsi <- land_17_18_19%>% 
  filter(total_land_cultivated_year>0) %>%
  group_by(year,TreatmentControl, household_questionnaire_id) %>%
  summarise(irrigated=sum(irrigated_out_of_tot_land_cult,na.rm = T)*0.0338) %>% 
  group_by(TreatmentControl,year) %>%
  summarise(N=n(), Mean=mean(irrigated)) %>% 
  mutate(across(is.numeric, round, 2))


lsiC <- lsi[1:3,-1]
lsiT <- lsi[4:6,3:4]
lsiC_lsiT <- cbind(lsiC,lsiT)

kable(lsiC_lsiT, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
column_spec(1, bold = T) %>%
kable_styling(latex_options = "striped", position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>%column_spec(3,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")
```

&nbsp;

Table : Time to irrigate 1 ha [6.21]
```{r irrigate 1 ha [6.21], echo=FALSE}

```
  TreatmentControl  year     N  Mean
  <chr>            <dbl> <int> <dbl>
1 Control           2017    94  94.9
2 Control           2018    94  93.2
3 Control           2019    92 103. 
4 Treatment         2017    22 124. 
5 Treatment         2018    22 127. 
6 Treatment         2019    23 180. 






Table 4.1: By year [5.0]
```{r irri By year [5.0], echo=FALSE}
 asy<- Agriculture_17_18_19%>% 
  group_by(year,TreatmentControl, household_questionnaire_id) %>% 
  summarise(hr_per_ha=mean(hrs_irr_1katha)/0.0339,irrigate_hr=sum(irri_for_season)) %>% 
  summarise(N=n(),average_hr_per_ha=mean(hr_per_ha,na.rm = T),
            total_irrigate_hr=mean(irrigate_hr,na.rm = T)) %>% 
  mutate(across(is.numeric, round, 2))


```
&nbsp;

>Table 4.2: By seasons [5.0]

```{r irri By seasons [5.0], echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
lsas <- Agriculture_17_18_19 %>% filter(season_of_crop!="Annual") %>% 
  group_by(year,season_of_crop,TreatmentControl,household_questionnaire_id) %>%
  summarise(hr_per_ha=mean(hrs_irr_1katha)/0.0339,irrigate_hr=sum(irri_for_season))%>% 
  group_by(TreatmentControl,season_of_crop,year) %>%
  summarise(n=n(),average_hr_per_ha=mean(hr_per_ha,na.rm = T),
            total_irrigate_hr=mean(irrigate_hr,na.rm = T)) %>% 
  mutate(across(is.numeric, round, 2))

lsasC <- lsas[1:9,-1]
lsasT <- lsas[10:18,4:6]
lsasC_lsasT <- cbind(lsasC,lsasT)


kable(lsasC_lsasT, "latex",col.names = c("Season","Year","N","mean 1 ha","Total","N","mean 1 ha","Total"), booktabs = T,align = "lcccccc",linesep = "") %>%
column_spec(1, bold = T) %>%
collapse_rows(columns = 1, valign = "top") %>% 
kable_styling(latex_options = "striped",stripe_index = c(3,6,9), position = "left") %>% 
column_spec(1:7, width = "1.5cm",border_left = F) %>%column_spec(5,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 2, "Control" = 3, "Treatment" = 3), bold = F, align = "c")

```


# Irrigation Intensity 

by year[4.0]
```{r year irri_intensity [4.0], echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}


```

by season [4.0]
```{r seasons irri_intensity [4.0], echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}


```

## fuel use
Table :Total litres of diesel/kerosene consumed for agriculture pumps in a YEAR [7.16] 
```{r fuel use Year [7.16], echo=FALSE}



```




&nbsp;


Table :# fuel use by the 'Water_extraction_mechanism'files- [6.2] 
```{r fuel use Season & Year  [6.2] , echo=FALSE}


```
  TreatmentControl  year Monsoon Summer Winter  Year
  <chr>            <dbl>   <dbl>  <dbl>  <dbl> <dbl>
1 Control           2017    48.5   29.8   26.4  95.8
2 Control           2018    41.5   19.0   28.7  74.6
3 Control           2019    44.8   29.3   67.9  98.4
4 Treatment         2017    36.1   42.3   49.6 116. 
5 Treatment         2018   100.    78.6   10.7 184. 
6 Treatment         2019    82.5   48.5   51.5 182. 


## aquaculture


